### 2010-09-17 proposal/proposal.tex
Moved to more appropriate name

To evaluate our system, we will have three main metrics: speed, number
of failures, and efficiency, which will be compared to its initial
hard-coded walking, and compared to other quadraped robots in the lab:

@@

>>>>

We will need to evaluate our system for two separate reasons.  First,
our learning methods depend on knowing the current performance of the
robot.  In order to optimize this performance, the learning algorithms
themselves will need access to the metrics of interest.  Of course,
the other reason for evaluation is to assess the performance of the
system as a whole.

For this latter purpose, we propose the use of three main metrics:

@@

\noindent We anticipate comparing our results along these dimensions
to a hard-coded walking configuration, as well as possibly to other
quadraped robots in the lab:
